MS-4.2 Types of Relationships

### 2020-04-25 ms-a4-2_non-linear-relationships.rmd
Added additional resources pages

---
title: "MS-4.2 Types of Relationships"
output:
  html_document:
    code_folding: "hide"
header-includes:
- \ifdefined\HCode\def\pgfsysdriver{pgfsys-dvisvgm4ht.def}\fi
- \usepackage{tikz}
---

@@

<div id="exp1"></div>

<script>
var exp1 = {
"id": "exp1",
"width":1406,
"height":718,
"showMenuBar":true,
"showAlgebraInput":true,
"showToolBar":true,
"customToolBar":"0 77 73 62 | 1 501 67 , 5 19 , 72 75 76 | 2 15 45 , 18 65 , 7 37 | 4 3 8 9 , 13 44 , 58 , 47 | 16 51 64 , 70 | 10 34 53 11 , 24  20 22 , 21 23 | 55 56 57 , 12 | 36 46 , 38 49  50 , 71  14  68 | 30 29 54 32 31 33 | 25 17 26 60 52 61 | 40 41 42 , 27 28 35 , 6",
"showToolBarHelp":true,
"showResetIcon":false,
"enableLabelDrags":false,
"enableShiftDragZoom":true,
"enableRightClick":false,
"errorDialogsActive":false,
"useBrowserForJS":false,
"allowStyleBar":false,
"preventFocus":false,
"showZoomButtons":true,
"capturingThreshold":3,
// add code here to run when the applet starts
"appletOnLoad":function(api){ /* api.evalCommand('Segment((1,2),(3,4))');*/ },
"showFullscreenButton":true,
"scale":1,
"disableAutoScale":false,
"allowUpscale":false,
"clickToLoad":false,
"appName":"graphing",
"showSuggestionButtons":true,
"buttonRounding":0.7,
"buttonShadows":false,
"language":"en",
// use this instead of ggbBase64 to load a material from geogebra.org
// "material_id":"RHYH3UQ8",
// use this instead of ggbBase64 to load a .ggb file
// "filename":"myfile.ggb",
"ggbBase64":"UEsDBBQACAgIAFFgl1AAAAAAAAAAAAAAAAAXAAAAZ2VvZ2VicmFfZGVmYXVsdHMyZC54bWztml1T4zYUhq+7v0Kjq/aCxHZiEhjMDrsznTLDskxhdnqr2CeOiiO5kkwcfv3KkmM7EKchZJuwhQuU4+jDet6joyM7Zx/zaYIeQEjKWYDdjoMRsJBHlMUBztT4aIg/nn84i4HHMBIEjbmYEhVgv6hZtdNWxx8Mi2skTQMcC5JOdBcYpQlRRZsAzzBCuaSnjF+TKciUhHAbTmBKrnhIlOlmolR62u3OZrPOYsAOF3FX9ym7uYy6caw6usRI3zWTAS4/nOp+l1rPeqad5zhu968vV3acI8qkIiwEjPSMIhiTLFFSf4QEpsAUUvMUApxyyhRGCRlBEuCbwkK/jgXAbxiVjTQoB59/+OVMTvgM8dHfEOprSmRQtTNGt6ijv/7MEy6QCLDnYhQXrXU50uWJp4El6YQE2LG1EzIHgR5IUl0hmeKh6cBcHZNEwqKuHuoLj8B+0y/rMzo1PJFUoLVwOnowmQJEekBcTtI1ysyNyo0eQ85FJFEe4GtyjdG8LB9taaoYPLf0sRzUb15V8wQa937WLcluxjiCFFikKy2BdrcCfTIwoItiZIt3zGsxH79jbsfsvpzzV9ak672ZaPEmnPiS/Qmxvucm4t474l0iXvbf/v8TrqliMcrif4BDPk0TyHfIPqGs5nhljIq7t12W4RjsjoHu7CkkO1tDL4BYfGpCw3sGUhZs636LD3/QSG9hZjyuM0mqdE/uYGh7gH/YkmiZBLFehHHGQmUCSgn2cyYemkr0+s4+tKj73Nr7W4TYmrLn9NezlBAXVsXldmHXbr1dTvfu1qvdWlPKVFLc0yVT+kQGxpXls2nfA6R3epCv7E4QJotT2bKXtWsqyHydnv5b0PNdzafR7vobEZVGmT4TjPWsoqaw2yVVTWE936+l7Xj+vtV9wR6wksh2mdDBuvoL/Xg3bnW8Xbwodp6VGDuDA3arBz09XvP4Vpp1ZvEmcrwDC54rEnMiFEhK2L+ddJJ53FjjNwu70mNg9XhtfrTb01LHdeyf2z9xXPfY9fYt9HrES4eam+pCDdl9HeTKEQ582WyeQ7bzDDmjYX0wsVZFsv+ThY8dJFY0BmajrkQod0y1uWMaPzrlO47cNfbcNd8+uvayaa9vXNAcXdgWF7bihWeLni36tvArQC8/chpZUx21Gon1k62hv9056W0Fkl2E2oOS/D9I4Fk2BdEICtcLu3Id34YF3V8GS7JuEATafKTdI2RCI+0+U6oFOtLKTUluFCQjyZNMwW0oAFj9ns868YxGalKoqMce07xwFdsnmnBBHzlTFQ1UrIGLxLwRXHoqssp1vHXp65Kjvi4wExYn9Vq8sFatgH3mbyo9fRq4SpgmQ6dEeNzxhj136PecgTs48YfHGyJ1hzVS+8XGRH+If7xohXvNoO73yr5FWD9o7Tk7VvLZ0e/36kJ9aDnE539G42dVf9ijvYSHmawfVlurIjT8yVIRkuU0oUTMX+fPK5KUdsIK8johuDNG4zcHBwi4fSoae1zf2qW1Gu/17WTGVFNkZKob2EEo+0TC+1jwjEXPN5qdTN3dt2+1QxtxngCpA9Gnhd14l/xsa28DVO6m+1x94QTC+xHPl3aj9TGGynoFXBmj8ZJ3xQrYfJbFAlqe59HeXWGbR3Btbx5X5hpN0t3Gj566i19YnX8HUEsHCGqraC7bBAAABCYAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFwAAAGdlb2dlYnJhX2RlZmF1bHRzM2QueG1s7ZjdbtMwFMev4Sks39PYaZIu0zJUwQVIMIF2w62XnLaGxA62uzZ7Nd6BZ+LEzroUNsSqbRKIXPT46xzHv79zEvfk5bapySUYK7UqKJ8wSkCVupJqWdC1W7w4oi9Pn58sQS/hwgiy0KYRrqBpP3Lnh7VJOjvq20TbFnRpRLvCEJS0tXC9T0E3lJCtlcdKn4kGbCtKOC9X0Ih3uhTOh1k51x5H0WazmVxPONFmGWFMG21tFS2XboKWErxrZQs6FI4x7p73Zur9YsZ49On9uzDPC6msE6oESnBFFSzEunYWi1BDA8oR17VQ0FIrWU5xjlpcQF3Qt8rhMqHsb5GUa3OJ/oNzQac8ZfT0+bMTu9Iboi8+47iCOrOGnb+vRP0Y7H6la22IKWjMKUHCnKG9QJvHiK5uV6KgbMJZuHiSM84zHgf/WnRgyKXAoCy0iLXTpQ/pWxeitnA9Fid/rysIPckwXsnGsybWAeqEk9sWoPKlsHzmNeu8/uN4UsG562ogbiXLLwos4k9HTn3hjawq6LdR8AG5BHWJRLSxqD3zs3TMD79iw27bcl/vuO+94qHZ++OtGrkl8+AxDwPncTDTYJJg0h0S+KrCfdr+F/ewBdP3nESDzL8ILrbSjvSe99XXexqz6UEaMy8x8wKzG3kfS0zcN48r509kW2HwQUaJSpwjlAFX/f3b73H7R6gUxoGVQo3Av+o7fiaf/Q3kH5P73SAxvoIRvw++vscPE+BB/PLcA4x57hF6u8tO6UNhLLU2lSXbgp6JM0wBg70a7CZYP3Qh+jfSMNud+fE2uOxAuLruVlAZrW74jppuEE8HxIc8UQ/60kgGKGmesSRLHkylQzf7vdjOTbmSDVQg9uGitE8HN9BNZh5ub/4Nth86zM2y2uf6lJs2JJM8cI3ZP8PVSNvsU+VPSDULKTpQzbO/kqoCt1vnWV8e59X0f169H82va1H5r7FhsR+v62Oq/MDjyt3JMUvy/pplPD3iScwfCtBjHDluPXD0jeFU0QVzFe8C3vcMQuZZMLNgjoLJ7zyfyKatZSnd76W1a7PAA/Ntn81D177KyWEqo9+tH86T2Z9u+5vAT3Ro4X/6fReNTvzR9d8Lpz8AUEsHCBnmYOpCAwAAAREAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAAFgAAAGdlb2dlYnJhX2phdmFzY3JpcHQuanNLK81LLsnMz1NIT0/yz/PMyyzR0FSorgUAUEsHCNY3vbkZAAAAFwAAAFBLAwQUAAgICABRYJdQAAAAAAAAAAAAAAAADAAAAGdlb2dlYnJhLnhtbL1YW2/bNhR+bn/FgZ42IIlJSpTkwu6QpBs2oO2KZRuGPQygJdrmIkuCRMdO0R+/c0hJlnMpmqZYGpUieXgu37lRmf2w3xRwo5vWVOU84GcsAF1mVW7K1TzY2uVpGvzw+uVspauVXjQKllWzUXYeSKIczuHsTCYpram6ngerRtVrZBFAXShLZ+bBLgCTz4M3l2nEfpLhqWTTi9PoMr08PX8j35zKVFywy+TyR8HiAGDfmldl9V5tdFurTF9la71Rb6tMWSdwbW39ajLZ7XZnvWpnVbOaoPR2sm/zyWq1OMMxALSvbOdB9/IK+R6d3oXunGCMT/5699bLOTVla1WZ6QDI9q15/fLFbGfKvNrBzuR2jUhFpOZam9Ua0Uh4GsCEqGqEpNaZNTe6xbOjqbPeburAkamS9l/4NygGwwLIzY3JdTMP2BkLp6mYhkxM04RPk0QEUDVGl7Yj5p3QSc9udmP0zvOlNycyYtMEXWVasyj0PFiqokW7TLlsENxh3trbQi8UirXNFucHjfiJ+4ck5qMmduhkjwXuMXZCT4KPlMyrM5ItOapsq6pwnBl8Ag6S4QN8CicQJ7gigEuIcCXFlQRCWpM8ghCIhIcQRThGtMxj3KFt/B/FAee4A4KBECA4iBCnUoJEsoTOCqSNp44fw4eoUSN8QloLQ3zcWhjhI+gNGUnPBvWQYezeJFEjfynIArcYphBNURAtyIRDiDrgPGGAHENiz50dEQP65RARe5GASAH5oenEmYmnOKZbuOOZ3i/yIb/E+DiH3fFLdOwVdAJD205o4H4QfpX5KQv9IPwQ+UF6msifjDypN5RFniYKn2thb1/4FPvSkX2cjEB/kPZuCIH05k5/GqJuGvupCzTGWbea+tUpTeNnGhN+lTF8JNUn51OE9iJ5KJ8g83mBebAzfYqdz4T3QXAlFib6dc89keGT7LxXGb9CYnyUet/G4Cj9YvFcpP+7zIQ9WG38yLvx2zhi+uWOeG5lGoCQnxc5m/Q9edaBAO2aaLtUtnrTEixJAkkIsRh6ZEwtrGuUiYBEQhKP2uUJNcxYHnomdcz0qGfK9LhxxrSYuC6MfYp6nu+gIuqb6EnXRj/da6PY9aJD40MFiRUHwEYNMdXIrgOiFmLogUJSGxQxYJ+UAmKqw4+0Q7wpVq0ZsF3roh5QdzCast7aI+iyTd6/2gqpVeHugR19XmXXFwPYHSetWjtmizenwwXN36SO7m8vZoVa6AJvslcUCgA3qiD9nIRlVVroq2scOHburjjT26wwuVHln+j6/lr2frtZ6AbcazUwoeMwXCpdjR5fKh1NVlVNfnXbYqjA/m/d4Ok4kQHcdu+C6m2mKJCj6dl0/IM3v9tHttLYc9c3V9paNLEFtddtD+mqoSzpoKLJL+1FVRyW6sqU9lLVdtu4bwXUoSG9z8tVoR1azpF4n86uF9X+ysEkYs/r99saZ6cdBovVZVVUDWCeCYl2rbpx4UdHQ6oNVMzRMEfB/D5xHfb5VDgKNy786KjQk163zlTe28l6KaYFPz8KNRcFdDnflsa+7SfWZNcHS4ne+7jH8Jgl/xYsuyy50efI9iBmNrkTcrO2brTK27XWtg/Co1AbxVlnOx5YXuqiuBqTJffpWl1QflQlwPoqa6qi8I1s9J5VxXZTOgdDQyZ7T88m97SadUnb67ipcu2TLPQnjvZn17opdeFzosSY3Vbb1pP7qHQKblv9Qdn1eZn/pleo5wdFRd0iiJ704JtcZ2aDB7u0DjuPUQT/gV7xy7leNbp3ptfGh1CnJoyMGkDyKXsg67GzqsEMQaEOwCN1ZpPeuplV2JVcp9oYghGjeKP27laGRaDuiseszRpTU+bCAhvTtT4kZ25aYpGPcCHEWpTlXWeNpRjDz/WtXVeN++5UllaofBV6gx+ZYF2WltuNbkw2RKxyH7Co+ra37Yx3SUrxCtXiX4yPO2F+wBy3H8ljUEW9Vo4f8z88mjLOY95nr7qlAjrC03F/N8RMX1ML+oD22LEOOvSTWrQYl1ZjoGpdHv6W4BXtAl5Q30b6GIdb/JDAc0uzH0GLaJmPGHyD61yWnvvAGBt6qDV2jVmNH+hUcOgu5GDtXn42ea7LQXU1xAZ2Ie2rxkBfIwCu1o7S3ruKnLbHMGzpzzE95kvsd3vqot/tv4c5qH9w9F3v2MHLbemCIjgc/Lwz+2Z6Qx+S95waxb72Cl/B5cixn3Xjr8tlqy1hLzz2p2L6oJe7aHBuuZvRD4IuH8Ucqlplxt6SzOguopNxxrjm3v2l6fV/UEsHCJxE9uqtBgAANhMAAFBLAQIUABQACAgIAFFgl1Bqq2gu2wQAAAQmAAAXAAAAAAAAAAAAAAAAAAAAAABnZW9nZWJyYV9kZWZhdWx0czJkLnhtbFBLAQIUABQACAgIAFFgl1AZ5mDqQgMAAAERAAAXAAAAAAAAAAAAAAAAACAFAABnZW9nZWJyYV9kZWZhdWx0czNkLnhtbFBLAQIUABQACAgIAFFgl1DWN725GQAAABcAAAAWAAAAAAAAAAAAAAAAAKcIAABnZW9nZWJyYV9qYXZhc2NyaXB0LmpzUEsBAhQAFAAICAgAUWCXUJxE9uqtBgAANhMAAAwAAAAAAAAAAAAAAAAABAkAAGdlb2dlYnJhLnhtbFBLBQYAAAAABAAEAAgBAADrDwAAAAA=",
};
// is3D=is 3D applet using 3D view, AV=Algebra View, SV=Spreadsheet View, CV=CAS View, EV2=Graphics View 2, CP=Construction Protocol, PC=Probability Calculator DA=Data Analysis, FI=Function Inspector, macro=Macros
var views = {'is3D': 0,'AV': 1,'SV': 0,'CV': 0,'EV2': 0,'CP': 0,'PC': 0,'DA': 0,'FI': 0,'macro': 0};
var applet = new GGBApplet(exp1, '5.0', views);
window.onload = function() {applet.inject('exp1')};
applet.setPreviewImage('data:image/gif;base64,R0lGODlhAQABAAAAADs=','https://www.geogebra.org/images/GeoGebra_loading.png','https://www.geogebra.org/images/applet_play.png');
</script>

>>>>

---
title: "MS-4.2 Types of Relationships"
output:
  html_document:
    code_folding: "hide"
---

@@

```{r}
library("ggplot2")
eq = function(x){2^x}
ggplot(data.frame(x=c(-3, 3)), aes(x=x)) + 
  stat_function(fun=eq)
```
